Graded Call-By-Push-Value

### 2020-07-10 popl21/popl21.tex
[ popl21 ] typos fixed after submission

Our style of coeffect typing is heavily influenced by
\citet{mcBride:wadler60} and \citet{atkey:lics18} who separate the
quantification of variable \emph{usage} $\gamma$ from the variable
\emph{declaration} in an ordinary typing context $\Gamma$.  This
division of labor removed a major obstacle in the integration of
linear and dependent types: the customary sorting of linear and
unrestricted variables into separate typing contexts, and the
dominance of context concatenation operations in the typing of
multiplicative connectives in linear logic, \eg:
\[
  \ru{\Delta_1 \vdash v_1 : A_1 \qquad
      \Delta_2 \vdash v_2 : A_2
    }{\Delta_1.\Delta_2 \vdash (v_1, v_2) : A_1 \otimes A_2}
\]
In contrast, the coeffect type systems of
\citet{reedPierce:icfp10},
\citet{orchard:icfp14},
\citet{brunel:esop14},
\citet{ghicaSmith:esop14}, and
\citet{orchard:icfp19}
keep context concatenation which does no harm in simply-typed settings
but seems to duplicate a mechanism already present in form of the
resource qualifier $0$.

>>>>

Our style of coeffect typing is heavily influenced by
\citet{mcBride:wadler60} and \citet{atkey:lics18} who keep the
quantification of variable \emph{usage} in usage context $\gamma$
separate from the variable
\emph{declaration} in an ordinary typing context $\Gamma$.  This
division of labor has removed two major obstacle in the integration of
linear and dependent types: the customary sorting of linear and
unrestricted variables into separate typing contexts, and the
dominance of context concatenation operations in the typing of
the multiplicative connectives of linear logic, \eg:
\[
  \ru{\Delta_1 \vdash v_1 : A_1 \qquad
      \Delta_2 \vdash v_2 : A_2
    }{\Delta_1.\Delta_2 \vdash (v_1, v_2) : A_1 \otimes A_2}
\]
In contrast to our style, the coeffect type systems of
\citet{reedPierce:icfp10},
\citet{orchard:icfp14},
\citet{brunel:esop14},
\citet{ghicaSmith:esop14}, and
\citet{orchard:icfp19}
keep context concatenation. This does no harm in simply-typed settings,
but seems to duplicate a mechanism already present in form of the
resource qualifier $0$.
